Think again?\\ Optimal mental simulation tracks problem difficulty

### 2015-02-02 manuscript.tex
typo

In addition, we found that response time is affected by the number of bounces during feedback.
Participants were fastest to respond on trials with zero bounces (\RTZeroBounces{}), slower to respond on trials with once bounce (\RTOneBounces{}), and slowest to respond on trials with two bounces (\RTTwoBounces{}).
While this may be partially modulated by difficulty---people make more variable predictions as bounces are added \cite{Smith:2013fc}, and more variable trials have longer reaction times---there appears to be an additional time cost.
For each number of bounces, we fit participants' response times to a second-order polynomial function of their responses.
From these fits, we see that the intercepts increase as a function of the number of bounces: for zero bounces, the intercept was \InterceptZeroBounces{}; for one, \InterceptOneBounces{}; and for two, \InterceptTwoBounces{}.
This suggests that it takes additional time to resolve a collision between the ball and a wall in the course of a simulation.

>>>>

In addition, we found that response time is affected by the number of bounces during feedback.
Participants were fastest to respond on trials with zero bounces (\RTZeroBounces{}), slower to respond on trials with one bounce (\RTOneBounces{}), and slowest to respond on trials with two bounces (\RTTwoBounces{}).
While this may be partially modulated by difficulty---people make more variable predictions as bounces are added \cite{Smith:2013fc}, and more variable trials have longer reaction times---there appears to be an additional time cost.
For each number of bounces, we fit participants' response times to a second-order polynomial function of their responses.
From these fits, we see that the intercepts increase as a function of the number of bounces: for zero bounces, the intercept was \InterceptZeroBounces{}; for one, \InterceptOneBounces{}; and for two, \InterceptTwoBounces{}.
This suggests that it takes additional time to resolve a collision between the ball and a wall in the course of a simulation.
